---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# QuarantineAnalysis

This R package provides both curated datasets and an interactive Shiny application to explore COVID-19 quarantine events and estimated risks across Australian states and territories. It is designed for **ETC5523 Assignment 4**, but also serves as a general-purpose educational tool for understanding how quarantine breaches and modeled risk can be analyzed over time.

## Installation

You can install the development version of this package from GitHub with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ETC5523-2025/assignment-4-packages-and-shiny-apps-laihoangson")
```

## Usage

Once installed, you can load the package and launch the interactive Shiny app.

```{r, eval = FALSE}
library(QuarantineAnalysis)  

# Launch the interactive application
launch_app()

# You can also directly access the data
head(breaches_data)
head(data_time)
```

## Key features

Key features include:

Curated Datasets

- `breaches_data`: Individual quarantine breach events, including state, date, facility, variant, vaccination status, and onward transmission information.

- `data_time`: Daily estimated quarantine risk aggregated by state and nationally, allowing time-series analysis of potential system failures.

Interactive Shiny Application

- Visualize monthly quarantine breaches as a bar chart.

- Explore estimated total quarantine risk over time as a line plot.

- Filter by state and date range to examine trends for specific regions.

- Display raw data in searchable and sortable tables for transparency and reproducibility.

## Documentation Website

A full documentation website created with **pkgdown** is available here:  

[https://etc5523-2025.github.io/assignment-4-packages-and-shiny-apps-laihoangson/](https://etc5523-2025.github.io/assignment-4-packages-and-shiny-apps-laihoangson/)
