---
title: "Data Description"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Data Source

The datasets are sourced from the following article:

Zachreson, C., Shearer, F. M., Price, D. J., Lydeamore, M. J., McVernon, J., McCaw, J., & Geard, N. (2022). COVID-19 in low-tolerance border quarantine systems: Impact of the Delta variant of SARS-CoV-2. *Science Advances, 8*(15), eabm3624. <https://doi.org/10.1126/sciadv.abm3624>

## The Breaches Dataset 

The `breaches_data` dataset contains detailed information on individual quarantine breach events in Australia. It has 39 rows and 9 columns.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(tibble)

tribble(
  ~Column,    ~Description,
  "no",       "Record number",
  "state",    "State or territory code",
  "date",     "Date of the breach",
  "facility", "Facility where breach occurred",
  "case_name","Role of the person involved (e.g., staff, security)",
  "variant",  "COVID-19 variant (if known)",
  "onward",   "Whether onward transmission occurred (TRUE/FALSE)",
  "vax",      "Vaccination status",
  "link",     "Reference link"
) |>
  kable()
```

## The Quarantine Risk Dataset

The `data_time` dataset contains aggregated information on estimated quarantine risk over time. It has 1,946 rows and 4 columns.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tribble(
  ~Column,      ~Description,
  "report_date","The date of the risk estimate",
  "state",      "State code (or \"AUS\" for the national total)",
  "total",      "Estimated total quarantine risk - the modelled likelihood that the quarantine system could lead to community transmission",
  "breach",     "Estimated risks associated with quarantine system failures (may be missing)"
) |>
  kable()
```

